\section{Technologies}

\subsection{Traffic Management Platforms}
A traffic management platform is a system where all the data collected on the road, by cameras, sensors, users' smartphone data etc. are combined and monitored. Identifying congested areas, traffic jams or accidents, a (human) "controller" may make some decisions in order to resolve the problems that occurred and ease the traffic flow. Often, there is also some Machine Learning involved, recording the effects of a certain regulation measure and later, when enough data has been gathered, suggests or performs certain regulations that might be especially effective.
In the past few years, Traffic Management Platforms have implemented by companies such as \textit{Hitachi (City Management Platform)} \cite{cityManagementPlatform} and \textit{Ericsson (Connected Traffic Cloud} \cite{ericsson}.

\subsection{Car-to-X Technology}
\textit{Car-to-X} is the term for inter-vehicle communication and communication between vehicles and infrastructures, such as traffic management platforms or other, maybe also, cloud-based infrastructures.\\
Cars receiving information from other cars or an information infrastructure are getting warnings, measures etc. accordingly.\\
This technology is the one that is considered to be leading in the direction of self-driving cars, but it may already be useful now, just for making predictions.

\subsection{Security and Privacy Requirements}
As this system highly depends on its users, privacy is a big issue, such a big issue, that some literature, \cite{book}, look as privacy as an aspect aside security.
Basically, the system/network should ensure the following \cite{book}:
\begin{enumerate}
    \item Sender Security is fulfilled
    \item The message is fresh and has not been altered by anyone
    \item The network is continuously available for communication
    \item The message is sent confidentially
    \The sender is anonymous
\end{enumerate}
 
 Here, the first two points are addressing the goals of security whereas poins 3 and 4 cover the privacy.